|

### 2024-11-08 manuscript/paper.Rmd
updated.

## Missing Data Imputation
\textcolor{red}{Greg, WE NEED RESULTS SECTION DESCRIBING THE RESULTS OF AKHIL'S MULTIPLE IMPUTATION, BOTH THE TESTS OF HOW WELL THE MODEL WORKED CLASSIFYING MODEL SAMPLES, AND SUMMARY STATISTICS OF FOSSIL IMPUTATION RESULTS -YS}

>>>>

## Missing Data Imputation
```{r echo = FALSE}
#Summaries
dat <- read.csv("Data/updated_stickle_imputations_100.csv")

```{r eval = FALSE}
library(mixgb)
library(mice)
library(tidyverse)
library(janitor)
library(missMethods)
library(ROCR)

stickle <- read_csv('./Data/Stickle_revamped.csv')

stick

extant_stickle <- stick %>% filter(gender != "Fossil") %>% select(!univID)
extant_stickle
summary(extant_stickle)

M = 10
k = 5
stick_matrix <- matrix(NA, nrow=nrow(extant_stickle), ncol = M)
set.seed(12)
fold <- sample(1:k, size = nrow(extant_stickle), replace=TRUE)
for(i in 1:k){
extant_stickle_temp <- extant_stickle
extant_stickle_temp$gender[fold==i] <- NA
imputed_stick <- mice(extant_stickle_temp,m=M)
for(n in 1:M){

  complete_stick <- complete(imputed_stick, n)

  complete_stick$gender[fold==i]
  stick_matrix[fold==i, n] <- as.character(complete_stick$gender[fold==i])
}

}
pct_male <- apply(stick_matrix,1,function(x){
  mean(x == "Male")
})

imptest <- data_frame(truth = as.factor(extant_stickle$gender), pct_male)
save(imptest, file = "./Data/imptest.RData")
roc_pred <- prediction(imptest$pct_male, imptest$truth)

auc_rocr <- performance(roc_pred, measure="auc")
plot(performance(roc_pred, measure="tpr", x.measure="fpr"))

auc_rocr@y.values[[1]]

```{r}
load("./Data/imptest.RData")
roc_pred <- prediction(imptest$pct_male, imptest$truth)

auc_rocr <- performance(roc_pred, measure="auc")
perf <- performance(roc_pred, measure="tpr", x.measure="fpr")
plot(perf)
dat <- data.frame(fpr = perf@x.values[[1]], tpr = perf@y.values[[1]])
ggplot(aes(x = fpr, y = tpr), data = dat) + geom_path() + theme_bw() + xlab("False Positive Rate") + ylab("True Positive Rate") + geom_abline(slope = 1, lty = 2, color = rgb(0,0,0,0.2)) + coord_fixed()

total sampel size1181
fossils 814
extant 367
`r auc_rocr@y.values[[1]]`

\textcolor{red}{Greg, WE NEED RESULTS SECTION DESCRIBING THE RESULTS OF AKHIL'S MULTIPLE IMPUTATION, BOTH THE TESTS OF HOW WELL THE MODEL WORKED CLASSIFYING MODEL SAMPLES, AND SUMMARY STATISTICS OF FOSSIL IMPUTATION RESULTS -YS}
